`You Draw It': Implementation of visually fitted trends with \texttt{r2d3}

### 2022-07-05 2022-sdss-you-draw-it-manuscript.tex
Phrasing

{\textcolor{RedOrange}{We set out to implement}} `You Draw It', adapted
from the New York Times feature, as a way to measure the patterns we see
in data. Here, we provide technical details of the software development,
utilizing interactive graphics in R\cite{r-software}. We then share
results from our study which validates `You Draw It' as a method for
graphical testing {\textcolor{RedOrange}{on linear trends}} and apply an
appropriate data analysis method to the participant data.
{\textcolor{RedOrange}{We also briefly demonstrate the use of the 'You Draw It' method and analysis on nonlinear data.}}

>>>>

{\textcolor{RedOrange}{We set out to implement}} `You Draw It', adapted
from the New York Times feature, as a way to experimentally assess the
patterns we see in data. Here, we provide technical details of the
software development, utilizing interactive graphics in
R\cite{r-software}. We then share results from our study which validates
`You Draw It' as a method for graphical testing
{\textcolor{RedOrange}{on linear trends}} and apply an appropriate data
analysis method to the participant data.
{\textcolor{RedOrange}{We also briefly demonstrate the use of the 'You Draw It' method and analysis on nonlinear data.}}
